---
title: 'Multiple Correspondence Analysis'
author: 'Dataset df'
output:
  html_document: default
---
This dataset contains 10342 individuals and 59 variables, 2 quantitative variables are considered as illustrative, 5 qualitative variables are considered as illustrative.

- - -



```{r, echo = FALSE}
library(FactoMineR)
load('/home/gabriel/Workspace.RData')
```
### 1. Study of the outliers
The analysis of the graphs leads to detect outliers that strongly influence the results. First we will describe these outliers and then we will suppress them from the analysis.
Looking at the graph, we can note that 735 particular individuals strongly contribute to the construction of the plane. The cumulative contribution of these individuals to the construction of the plane equals **55.3%**.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(memory, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.1 - Individuals factor map (MCA) before correction.** 
*Highlighting of 735 outliers.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(res, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.2 - Individuals factor map (MCA) after correction.** 
*Highlighting of 735 outliers.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
c("scolarite_obtenue_2010_2e 3e cycle", "scolarite_avant_BAC", 
"scolarite_avant_<= DES", "scolarite_obtenue_2010_Cegep", "scol_pere_> BAC", 
"scol_mere_BAC", "scol_pere_< DES", "scol_pere_BAC", "Homme")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(memory, choix = 'ind', invisible = 'ind', selectMod = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (MCA) before correction**
*The factors in red are considered as active whereas those in green are illustrative.*
*The labeled variables are those the best shown on the plane.*

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
c("scolarite_obtenue_2010_2e 3e cycle", "scolarite_avant_BAC", 
"scolarite_avant_<= DES", "scolarite_obtenue_2010_Cegep", "scol_pere_> BAC", 
"scol_mere_BAC", "scol_pere_< DES", "scol_pere_BAC", "Homme")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(res, choix = 'ind', invisible = 'ind', selectMod = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (MCA) after correction**

- - -

**The individual 103** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 277** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 358** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 417** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 451** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010_inconnu*, *emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 565** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 595** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 609** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 632** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 745** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 754** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 927** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 976** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 1134** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 1183** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 1202** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 1253** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 1259** :

- is characterized by the factor(s) :
*langue_inconnu*, *scolarite_avant_DEP*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1271** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 1454** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 1512** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1515** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1575** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1590** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 1647** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 1808** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 1828** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 1955** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 2082** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 2121** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2200** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 2268** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 2294** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 2306** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 2318** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *scolarite_avant_Certificat*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 2403** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2433** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2534** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 2609** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 2678** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 2705** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2805** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 2834** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 2910** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2977** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2988** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3051** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3185** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 3188** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 3212** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 3278** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3322** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3422** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3423** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3487** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 3592** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3622** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 3633** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3676** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3747** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3794** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3856** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3970** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 4011** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 4049** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4069** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4219** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4287** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4353** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4576** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4592** :

- is characterized by the factor(s) :
*langue_inconnu*, *scolarite_avant_DEP*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4627** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4643** :

- is characterized by the factor(s) :
*langue_inconnu*, *scolarite_avant_Certificat*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4892** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4896** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4904** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4935** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5033** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5069** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 5082** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 5320** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 5422** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 5530** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 5564** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 5655** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 5673** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 5810** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 5824** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 5826** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 5828** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 5845** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 5864** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 5866** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 5884** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 5950** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 5952** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6016** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6117** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 6137** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6138** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6164** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6194** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 6254** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6259** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 6326** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6350** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 6586** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 6592** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6596** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 6627** :

- is characterized by the factor(s) :
*langue_inconnu*, *scolarite_avant_Certificat*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 6729** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 6775** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010_inconnu*, *emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6846** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 6850** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 6901** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7017** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7054** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7074** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 7433** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7476** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 7487** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7525** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7584** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 7708** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 7740** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7814** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7857** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 7916** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 7948** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 8013** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8065** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8168** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 8203** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8284** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8340** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 8448** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *scolarite_avant_Certificat*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 8454** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8534** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 8566** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 8653** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 8734** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8737** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8907** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 8918** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_3*, *scol_pere_CEGEP* (factors are sorted from the strongest).

**The individual 9020** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9099** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 9122** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 9475** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9488** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 9598** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 9600** :

- is characterized by the factor(s) :
*langue_inconnu*, *scolarite_avant_Certificat*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 9672** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 9673** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 9692** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 9975** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 10026** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 10042** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_3* (factors are sorted from the strongest).

**The individual 10146** :

- is characterized by the factor(s) :
*langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 10200** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *langue_inconnu*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 39** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 80** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 139** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_> BAC* (factors are sorted from the strongest).

**The individual 227** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 294** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 325** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 361** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 416** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 428** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 530** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 533** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 571** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 622** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 662** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 673** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 696** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 697** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_inconnu*, *langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 717** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 786** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 845** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 848** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_4*, *scol_pere_> BAC*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 900** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 914** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 964** :

- is characterized by the factor(s) :
*scol_mere_DEP*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1022** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1081** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1093** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1102** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 1109** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1127** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1142** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1152** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 1164** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1206** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1240** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1263** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1287** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1304** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 1322** :

- is characterized by the factor(s) :
*diplome_secteur_2010_10*, *langue_Autre langue*, *scol_pere_inconnu*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 1397** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1430** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 1468** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1469** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1511** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Aucun de ces choix*, *diplome_secteur_2010_3*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1532** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1549** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1571** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1657** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 1660** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 1671** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1821** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1845** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1856** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Autre langue*, *scol_mere_> BAC*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1913** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 1920** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1995** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 1996** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2019** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 2045** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2073** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2096** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 2136** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2181** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2187** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 2242** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2299** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2314** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2326** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_10*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2337** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2430** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2441** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2541** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_2*, *langue_Autre langue*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 2604** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2622** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2702** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2715** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 2721** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *langue_Francais* (factors are sorted from the strongest).

**The individual 2744** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2748** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 2760** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2937** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3023** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3038** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3098** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3140** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3193** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 3241** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3375** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3387** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3447** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 3471** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3482** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 3494** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3574** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3602** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 3605** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3637** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3688** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 3698** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3781** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3810** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3821** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 3972** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 4140** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4167** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4171** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4223** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4351** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 4387** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4440** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 4552** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4722** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4744** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4747** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 4776** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 4797** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4839** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4982** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 4997** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5164** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5208** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5281** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5307** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5440** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 5532** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5555** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5558** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 5562** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5683** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 5870** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5925** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 5990** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6017** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 6043** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6111** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6226** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 6235** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6383** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6493** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6529** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6531** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6546** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6639** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6641** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 6643** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6737** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_2*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 6784** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *langue_Autre langue*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 6792** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 6806** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6863** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6877** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_> BAC*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6883** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6905** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7011** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7035** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_> BAC* (factors are sorted from the strongest).

**The individual 7052** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7076** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7109** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7136** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7167** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7226** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 7232** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7281** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7478** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7617** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 7625** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_9*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 7705** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7733** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 7781** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7798** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7826** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue*, *scol_pere_CEGEP*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 7878** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 7932** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7945** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7952** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7995** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8057** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 8064** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8122** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8131** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8162** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8194** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *diplome_secteur_2010_7*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8229** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8230** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8263** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8301** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 8383** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8419** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8470** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8539** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8544** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8545** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8575** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8673** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8724** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8748** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_2*, *langue_Autre langue*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8752** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8757** :

- is characterized by the factor(s) :
*emprunt_gouv_inconnu*, *scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8767** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_3*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8772** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8777** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8829** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 8834** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_inconnu*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 8880** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8883** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8930** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8953** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9039** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 9041** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9052** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010_inconnu*, *scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9055** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_2*, *langue_Autre langue*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 9106** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9139** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scol_mere_inconnu*, *langue_Aucun de ces choix*, *diplome_secteur_2010_10*, *scol_pere_inconnu*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 9156** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9195** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 9197** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9206** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Autre langue*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 9225** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9331** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 9353** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 9358** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9381** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 9485** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 9529** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 9547** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9564** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 9616** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9634** :

- is characterized by the factor(s) :
*langue_inconnu*, *scol_mere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 9642** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9722** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9758** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 9797** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9823** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9862** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9894** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 10034** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 10046** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 10093** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 10116** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 10119** :

- is characterized by the factor(s) :
*scol_mere_inconnu*, *diplome_secteur_2010_10*, *scol_pere_inconnu* (factors are sorted from the strongest).

**The individual 10253** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 10254** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 10280** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 89** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 169** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_pere_< DES*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 285** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 384** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 387** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 478** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 594** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 744** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Aucun de ces choix*, *diplome_secteur_2010_1*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 984** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1131** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1138** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1149** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1160** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1198** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1247** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1260** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1331** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1450** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1498** :

- is characterized by the factor(s) :
*diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1505** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1625** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1773** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1788** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1884** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1903** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1997** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 2135** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 2145** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 2186** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2271** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2281** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 2389** :

- is characterized by the factor(s) :
*langue_Anglais et francais*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 2431** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_pere_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 2432** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2817** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2999** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3104** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scol_mere_> BAC*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3240** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scolarite_obtenue_2010_inconnu*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3247** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3648** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_DEP*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3699** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3717** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *diplome_secteur_2010_7*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3791** :

- is characterized by the factor(s) :
*diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3838** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3929** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 3943** :

- is characterized by the factor(s) :
*langue_Anglais et francais*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3961** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4012** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 4067** :

- is characterized by the factor(s) :
*diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4205** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_DEP*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4226** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4291** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4313** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4392** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4594** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4778** :

- is characterized by the factor(s) :
*diplome_secteur_2010_99*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 4795** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5038** :

- is characterized by the factor(s) :
*langue_Anglais et francais*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5072** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_pere_< DES*, *langue_Francais*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 5078** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5171** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5338** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5350** :

- is characterized by the factor(s) :
*diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5381** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5401** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5430** :

- is characterized by the factor(s) :
*diplome_secteur_2010_99*, *scol_mere_DEP*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5434** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5485** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5539** :

- is characterized by the factor(s) :
*diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5662** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *langue_Anglais et francais*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5729** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5765** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5805** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5835** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5900** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5923** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 5949** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 5974** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6030** :

- is characterized by the factor(s) :
*diplome_secteur_2010_99*, *scol_mere_DEP*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6049** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_3*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6104** :

- is characterized by the factor(s) :
*langue_Anglais et francais*, *scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6128** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6133** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6173** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_DEP*, *diplome_secteur_2010_1*, *scol_pere_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6197** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6247** :

- is characterized by the factor(s) :
*scolarite_avant_Certificat*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6287** :

- is characterized by the factor(s) :
*scol_mere_DEP*, *diplome_secteur_2010_10*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6339** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6365** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6554** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6798** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6803** :

- is characterized by the factor(s) :
*langue_Anglais et francais*, *minorite_visible_inconnu*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6845** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 6919** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7055** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7196** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7302** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 7304** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7335** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7340** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7406** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7497** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7501** :

- is characterized by the factor(s) :
*scol_pere_DEP*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7514** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7608** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7723** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_pere_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7729** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7770** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7843** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7856** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 7889** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7921** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_10*, *scol_pere_inconnu*, *scol_mere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8007** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 8035** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8146** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8205** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8466** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010_inconnu*, *scol_mere_DEP*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_pere_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8472** :

- is characterized by the factor(s) :
*scol_mere_DEP*, *scol_pere_DEP*, *diplome_secteur_2010_1*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8509** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8613** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8616** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8655** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Anglais et francais*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8711** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8773** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8788** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8802** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 8814** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_inconnu*, *scol_pere_inconnu*, *diplome_secteur_2010_9*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8839** :

- is characterized by the factor(s) :
*diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8853** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8882** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8914** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 8964** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9118** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9173** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9185** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9308** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 9322** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9408** :

- is characterized by the factor(s) :
*scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9430** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9461** :

- is characterized by the factor(s) :
*scol_mere_DEP*, *scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_pere_CEGEP*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9541** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_DEP*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9576** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9680** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9743** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 9748** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 9978** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 10037** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5*, *langue_Francais* (factors are sorted from the strongest).

**The individual 10124** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES*, *langue_Francais* (factors are sorted from the strongest).

**The individual 10196** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *diplome_secteur_2010_6*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 10286** :

- is characterized by the factor(s) :
*diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 65** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 138** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 153** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 196** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 204** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 275** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 299** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 392** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 396** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 399** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 439** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 769** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_1* (factors are sorted from the strongest).

**The individual 806** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 812** :

- is characterized by the factor(s) :
*diplome_secteur_2010_10*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 830** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 834** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 931** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 934** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 987** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 1012** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1021** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1076** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 1130** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1151** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1168** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1232** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 1323** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1336** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_pere_CEGEP* (factors are sorted from the strongest).

**The individual 1369** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_4*, *scol_pere_> BAC*, *langue_Francais* (factors are sorted from the strongest).

**The individual 1419** :

- is characterized by the factor(s) :
*scolarite_avant_Certificat*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1433** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_pere_inconnu*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 1455** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1526** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1583** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1584** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1606** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1650** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_10*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 1708** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 1759** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 1786** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 1804** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 1877** :

- is characterized by the factor(s) :
*scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 1952** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2120** :

- is characterized by the factor(s) :
*scolarite_avant_Certificat*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2137** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 2193** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2226** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2276** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2368** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2449** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2500** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2509** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2563** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_10*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2576** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2722** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2828** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 2861** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 2880** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 2901** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3078** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 3100** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3110** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3152** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 3190** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 3476** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 3550** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3624** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 3632** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3674** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3691** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 3734** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 3823** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 3894** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3906** :

- is characterized by the factor(s) :
*minorite_visible_inconnu*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3920** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Aucun de ces choix*, *diplome_secteur_2010_10*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 3926** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4015** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4043** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4117** :

- is characterized by the factor(s) :
*scolarite_avant_BAC+*, *langue_Autre langue*, *diplome_secteur_2010_3*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 4124** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 4173** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_pere_inconnu*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4256** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 4449** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 4453** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 4491** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 4538** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 4562** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4588** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 4619** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 4655** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4697** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 4728** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 4815** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4918** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 4986** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_5*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 5004** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5012** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5019** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *diplome_secteur_2010_2*, *scol_mere_> BAC*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 5121** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5145** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5155** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 5262** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 5288** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5298** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5310** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5336** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 5465** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 5494** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 5653** :

- is characterized by the factor(s) :
*diplome_secteur_2010_10*, *langue_Autre langue*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 5836** :

- is characterized by the factor(s) :
*langue_inconnu*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6035** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6054** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6120** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6246** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 6299** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6346** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6358** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 6362** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6405** :

- is characterized by the factor(s) :
*scolarite_avant_DEP*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6434** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6457** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 6650** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 6757** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 6857** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_4*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 6984** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7078** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7325** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 7482** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7500** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7548** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7670** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7803** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 7904** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 7960** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *scol_mere_> BAC*, *diplome_secteur_2010_1*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 7970** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 8040** :

- is characterized by the factor(s) :
*diplome_secteur_2010_10*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8050** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 8161** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8176** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_1*, *scol_mere_< DES*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8184** :

- is characterized by the factor(s) :
*scolarite_avant_doctorat*, *scol_mere_> BAC*, *diplome_secteur_2010_9*, *scol_pere_> BAC* (factors are sorted from the strongest).

**The individual 8195** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8252** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8257** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8268** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4* (factors are sorted from the strongest).

**The individual 8297** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8387** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8425** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8464** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 8477** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6*, *scol_mere_< DES*, *scol_pere_< DES*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 8557** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 8579** :

- is characterized by the factor(s) :
*diplome_secteur_2010_2*, *langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8643** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 8674** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8746** :

- is characterized by the factor(s) :
*scolarite_avant_Certificat*, *langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9* (factors are sorted from the strongest).

**The individual 8751** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8801** :

- is characterized by the factor(s) :
*scolarite_avant_Maitrise*, *langue_Aucun de ces choix*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 8837** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 8993** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9024** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 9050** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 9228** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 9247** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9269** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_CEGEP*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9271** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_6* (factors are sorted from the strongest).

**The individual 9274** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_pere_> BAC*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9323** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix* (factors are sorted from the strongest).

**The individual 9471** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 9516** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_pere_> BAC*, *scol_mere_CEGEP* (factors are sorted from the strongest).

**The individual 9520** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9569** :

- is characterized by the factor(s) :
*langue_Aucun de ces choix*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9638** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9648** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9693** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 9703** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 9850** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_9*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 9872** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Aucun de ces choix*, *scol_mere_< DES* (factors are sorted from the strongest).

**The individual 9890** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 10030** :

- is characterized by the factor(s) :
*diplome_secteur_2010_7*, *langue_Autre langue* (factors are sorted from the strongest).

**The individual 10075** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *diplome_secteur_2010_5* (factors are sorted from the strongest).

**The individual 10155** :

- is characterized by the factor(s) :
*langue_Autre langue*, *scol_mere_< DES*, *scol_pere_< DES*, *diplome_secteur_2010_4*, *scolarite_avant_CEGEP* (factors are sorted from the strongest).

**The individual 10210** :

- is characterized by the factor(s) :
*scolarite_avant_Certificat*, *langue_Aucun de ces choix*, *scol_mere_< DES*, *diplome_secteur_2010_8*, *scol_pere_< DES* (factors are sorted from the strongest).

**The individual 10251** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8* (factors are sorted from the strongest).

**The individual 10311** :

- is characterized by the factor(s) :
*langue_Autre langue*, *diplome_secteur_2010_8*, *scol_pere_> BAC* (factors are sorted from the strongest).

These outliers are suppressed from the analysis and a second one is performed on the rest of the individuals.

- - -

### 2. Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of analyse express **8.63%** of the total dataset inertia ; that means that 8.63% of the individuals (or variables) cloud total variability is explained by the plane.
This is a very small percentage and the first plane represents a small part of the data variability.
This value is greater than the reference value that equals **5.21%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 102 data tables of equivalent size on the basis of a uniform distribution).

From these observations, it is important to also interpret the dimensions greater or equal to the third one.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
ggplot2::ggplot(cbind.data.frame(x=1:nrow(res$eig),y=res$eig[,2])) + ggplot2::aes(x=x, y=y)+ ggplot2::geom_col(fill="blue") + ggplot2::xlab("Dimension") + ggplot2::ylab("Percentage of variance") + ggplot2::ggtitle("Decomposition of the total inertia") + ggplot2::theme_light() + ggplot2::theme(plot.title = ggplot2::element_text(hjust =0.5)) + ggplot2::scale_x_continuous(breaks=1:nrow(res$eig))
```

**Figure 2 - Decomposition of the total inertia**

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 17 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (50.89% against 42.15%).
This observation suggests that only these axis are carrying a real information.
As a consequence, the description will stand to these axis.

- - -

### 3. Description of the plane 1:2

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
res.MCA<-MCA(df[1:19][,-c(1,2,5)],quanti.sup=c(1,2),quali.sup=c(12,13,14,15,16),graph=FALSE)
plot.MCA(res.MCA,select= 'contrib 10342',selectMod= 'contrib  9 ',habillage='contrib',col.quali.sup='#006400',title="Df_statut_2013",label =c('var'))
```

**Figure 3.1 - Individuals factor map (MCA)**

The Wilks test p-value indicates which variable factors are the best separated on the plane (i.e. which one explain the best the distance between individuals).
```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
wilks.p <-
c(secteur_emploi_2013 = 0, lien_emploi_etude = 1.20293905520063e-84, 
sur_sous_qualification = 1.17552169338882e-44, etude_temps_plein = 7.43614439020453e-29, 
satisfaction_emploi = 5.29859358540475e-20)
wilks.p
```
The best qualitative variable to illustrate the distance between individuals on this plane is : *secteur_emploi_2013*.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
sample = sample(rownames(res$call$X), length(rownames(res$call$X)))
res$call$X = res$call$X[sample,]
res$ind$coord = res$ind$coord[sample[!sample %in% rownames(res$ind.sup$coord)],]
res$ind.sup$coord = res$ind.sup$coord[sample[sample %in% rownames(res$ind.sup$coord)],]
drawn <-
integer(0)
hab <-
"secteur_emploi_2013"
par(mar = c(4.1, 4.1, 1.1, 2.1))
plotellipses(res, axes = 1:2, invisible = c('var', 'quali'), select = drawn, keepvar = hab, title = '', cex = cex)
```

**Figure 3.2 - Individuals factor map (MCA)**
*The labeled individuals are those with the higher contribution to the plane construction.*
*The individuals are coloured after their category for the variable* secteur_emploi_2013.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
