---
title: 'Multiple Correspondence Analysis'
author: 'Dataset df'
output:
  html_document: default
---
This dataset contains 10342 individuals and 53 variables, 2 quantitative variables are considered as illustrative, 6 qualitative variables are considered as illustrative.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('/home/gabriel/Workspace.RData')
```
### 1. Study of the outliers
The analysis of the graphs does not detect any outlier.

- - -

### 2. Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of analyse express **16.11%** of the total dataset inertia ; that means that 16.11% of the individuals (or variables) cloud total variability is explained by the plane.
This is a very small percentage and the first plane represents a small part of the data variability.
This value is greater than the reference value that equals **5.99%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 110 data tables of equivalent size on the basis of a uniform distribution).

From these observations, it is important to also interpret the dimensions greater or equal to the third one.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
ggplot2::ggplot(cbind.data.frame(x=1:nrow(res$eig),y=res$eig[,2])) + ggplot2::aes(x=x, y=y)+ ggplot2::geom_col(fill="blue") + ggplot2::xlab("Dimension") + ggplot2::ylab("Percentage of variance") + ggplot2::ggtitle("Decomposition of the total inertia") + ggplot2::theme_light() + ggplot2::theme(plot.title = ggplot2::element_text(hjust =0.5)) + ggplot2::scale_x_continuous(breaks=1:nrow(res$eig))
```

**Figure 2 - Decomposition of the total inertia**

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 13 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (53.75% against 37.38%).
This observation suggests that only these axis are carrying a real information.
As a consequence, the description will stand to these axis.

- - -

### 3. Description of the plane 1:2

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
res.MCA<-MCA(df[1:19][,-c(2,3,4)],quanti.sup=c(1,2),quali.sup=c(3,4,5,6,7,8),graph=FALSE)
plot.MCA(res.MCA,invisible= 'var',select= 'contrib 10342',selectMod= 'contrib  8 ',habillage='contrib',title="DF_NAture Sociodem",label ='none')
```

**Figure 3.1 - Individuals factor map (MCA)**

The Wilks test p-value indicates which variable factors are the best separated on the plane (i.e. which one explain the best the distance between individuals).
```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
wilks.p <-
c(scolarite_avant = 1.49937600091776e-282, genre = 1.42976758501819e-71, 
scol_pere = 1.93260661831279e-27, scol_mere = 5.81962593281335e-23, 
minorite_visible = 9.01537671436044e-13, langue = 5.53693340642496e-12
)
wilks.p
```
The best qualitative variable to illustrate the distance between individuals on this plane is : *scolarite_avant*.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
sample = sample(rownames(res$call$X), length(rownames(res$call$X)))
res$call$X = res$call$X[sample,]
res$ind$coord = res$ind$coord[sample[!sample %in% rownames(res$ind.sup$coord)],]
res$ind.sup$coord = res$ind.sup$coord[sample[sample %in% rownames(res$ind.sup$coord)],]
drawn <-
integer(0)
hab <-
"scolarite_avant"
par(mar = c(4.1, 4.1, 1.1, 2.1))
plotellipses(res, axes = 1:2, invisible = c('var', 'quali'), select = drawn, keepvar = hab, title = '', cex = cex)
```

**Figure 3.2 - Individuals factor map (MCA)**
*The labeled individuals are those with the higher contribution to the plane construction.*
*The individuals are coloured after their category for the variable* scolarite_avant.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
