---
title: 'Classification'
author: 'Dataset res.PCA'
output:
  html_document: default
---
.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('/home/gabriel/Workspace.RData')
```

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
drawn <-
c("68", "72", "53", "87", "37", "70", "47", "90", "80", "1", 
"13", "73", "75", "92", "98", "9")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'tree', title = '')
```

**Figure 1.1 - Hierarchical tree.**

The classification made on individuals reveals 4 clusters.


```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'map', draw.tree = FALSE, title = '')
```

**Figure 1.2 - Ascending Hierarchical Classification of the individuals.**

The **cluster 1** is made of individuals such as *13* and *37*. This group is characterized by :

- high values for the variable *dette_2013*.
- low values for the variables *salaire_2013* and *age* (variables are sorted from the weakest).

The **cluster 2** is made of individuals such as *75* and *90*. This group is characterized by :

- high values for the variable *poids*.
- low values for the variables *emprunt*, *dette_2013*, *salaire_2013* and *age* (variables are sorted from the weakest).

The **cluster 3** is made of individuals such as *53* and *87*. This group is characterized by :

- high values for the variables *emprunt* and *dette_2013* (variables are sorted from the strongest).
- low values for the variables *age* and *salaire_2013* (variables are sorted from the weakest).

The **cluster 4** is made of individuals such as *1*, *9*, *47*, *68*, *70*, *72*, *73*, *80*, *92* and *98*. This group is characterized by :

- high values for the variables *salaire_2013* and *age* (variables are sorted from the strongest).
- low values for the variables *dette_2013*, *poids* and *emprunt* (variables are sorted from the weakest).

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = '3D.map', ind.names=FALSE, title = '')
```

**Figure 1.3 - Hierarchical tree on the factorial map.**

The hierarchical tree can be drawn on the factorial map with the individuals colored according to their clusters.


