---
title: 'Classification'
author: 'Dataset res.PCA'
output:
  word_document: default
---



.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('/home/gabriel/Workspace.RData')
```

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
drawn <-
c("30", "94", "19", "95", "2", "17", "26", "53", "81", "31", 
"40", "5", "46", "99", "98", "85")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'tree', title = '')
```

**Figure 1.1 - Hierarchical tree.**

The classification made on individuals reveals 10 clusters.


```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'map', draw.tree = FALSE, title = '')
```

**Figure 1.2 - Ascending Hierarchical Classification of the individuals.**

The **cluster 1** is made of individuals such as *81*. This group is characterized by :

- low values for the variables *salaire_2013*, *emprunt*, *dette_2013* and *poids* (variables are sorted from the weakest).

The **cluster 2** is made of individuals sharing :

- high values for the variables *dette_2013* and *emprunt* (variables are sorted from the strongest).
- low values for the variables *salaire_2013* and *age* (variables are sorted from the weakest).

The **cluster 3** is made of individuals such as *40*. This group is characterized by :

- low values for the variables *salaire_2013*, *emprunt*, *dette_2013* and *age* (variables are sorted from the weakest).

The **cluster 4** is made of individuals such as *2*, *17*, *26*, *85* and *94*. This group is characterized by :

- low values for the variables *emprunt*, *dette_2013*, *salaire_2013* and *age* (variables are sorted from the weakest).

The **cluster 5** is made of individuals such as *53*. This group is characterized by :

- high values for the variable *emprunt*.
- low values for the variables *age* and *dette_2013* (variables are sorted from the weakest).

The **cluster 6** is made of individuals such as *5*, *19* and *46*. This group is characterized by :

- high values for the variables *salaire_2013* and *poids* (variables are sorted from the strongest).
- low values for the variables *emprunt*, *dette_2013* and *age* (variables are sorted from the weakest).

The **cluster 7** is made of individuals such as *30*. This group is characterized by :

- high values for the variables *dette_2013*, *emprunt* and *salaire_2013* (variables are sorted from the strongest).
- low values for the variable *age*.

The **cluster 8** is made of individuals such as *95*. This group is characterized by :

- high values for the variables *salaire_2013* and *age* (variables are sorted from the strongest).
- low values for the variables *emprunt* and *dette_2013* (variables are sorted from the weakest).

The **cluster 9** is made of individuals such as *98* and *99*. This group is characterized by :

- high values for the variables *emprunt*, *salaire_2013* and *dette_2013* (variables are sorted from the strongest).

The **cluster 10** is made of individuals such as *31*. This group is characterized by :

- high values for the variables *salaire_2013* and *age* (variables are sorted from the strongest).
- low values for the variables *dette_2013*, *emprunt* and *poids* (variables are sorted from the weakest).

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = '3D.map', ind.names=FALSE, title = '')
```

**Figure 1.3 - Hierarchical tree on the factorial map.**

The hierarchical tree can be drawn on the factorial map with the individuals colored according to their clusters.


