---
title: 'Multiple Correspondence Analysis'
author: 'Dataset entrain_valid'
output:
  html_document: default
---
This dataset contains 10342 individuals and 21 variables, 2 quantitative variables are considered as illustrative, 6 qualitative variables are considered as illustrative.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('/home/gabriel/Workspace.RData')
```
### 1. Study of the outliers
The analysis of the graphs leads to detect outliers that strongly influence the results. First we will describe these outliers and then we will suppress them from the analysis.
Looking at the graph, we can note that 504 particular individuals strongly contribute to the construction of the plane. The cumulative contribution of these individuals to the construction of the plane equals **26.8%**.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(memory, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.1 - Individuals factor map (MCA) before correction.** 
*Highlighting of 504 outliers.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(res, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.2 - Individuals factor map (MCA) after correction.** 
*Highlighting of 504 outliers.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
c("emprunt_gouv_Non", "emprunt_gouv_Oui", "Cegep", "satisfaction_emploi.NA", 
"etude_temps_plein_Non", "etude_temps_plein_Oui", "satisfaction_emploi_Oui", 
"scolarite_obtenue_2010.NA", "1er cycle", "emprunt_gouv.NA")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(memory, choix = 'ind', invisible = 'ind', selectMod = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (MCA) before correction**
*The factors in red are considered as active whereas those in green are illustrative.*
*The labeled variables are those the best shown on the plane.*

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <-
c("emprunt_gouv_Non", "emprunt_gouv_Oui", "Cegep", "satisfaction_emploi.NA", 
"etude_temps_plein_Non", "etude_temps_plein_Oui", "satisfaction_emploi_Oui", 
"scolarite_obtenue_2010.NA", "1er cycle", "emprunt_gouv.NA")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.MCA(res, choix = 'ind', invisible = 'ind', selectMod = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (MCA) after correction**

- - -

**The individual 15** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 64** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 106** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 116** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 119** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 131** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 142** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 159** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 210** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 232** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 289** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 294** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 322** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 329** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 334** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 353** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 364** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 367** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 378** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 409** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 426** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 460** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 470** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 503** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 504** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 505** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 537** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 554** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 576** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 580** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 588** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 628** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 689** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 761** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 791** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 840** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 844** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 875** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 883** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 926** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 931** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 974** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 999** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1010** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1046** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1059** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1061** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1067** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1074** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1082** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1101** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1102** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1108** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1153** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1166** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1168** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1215** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1225** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1238** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1266** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1270** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1274** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1288** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1289** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1318** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1339** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1341** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1344** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1354** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1445** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1459** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1461** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1494** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1555** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1584** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1660** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1668** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1683** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1692** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1707** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1708** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1734** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1741** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1779** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1802** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1825** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1827** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1880** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1895** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1903** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1927** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1946** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1981** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 1996** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2019** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2021** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2034** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2052** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2066** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2138** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2185** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2259** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2260** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2288** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2295** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2314** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2315** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2359** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2370** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2380** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2389** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2399** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2414** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2424** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2442** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2453** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2461** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2478** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2560** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2599** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2606** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2610** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2617** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 2665** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2668** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2703** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2770** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2789** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2793** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2813** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2859** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2866** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2878** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2889** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2895** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2931** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 2944** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3009** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3061** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3122** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3170** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3190** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3199** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3259** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3265** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3274** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3285** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3311** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3315** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3317** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3332** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3350** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3355** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3378** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3437** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3576** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3667** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3682** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3688** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3702** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3727** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3741** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3760** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3764** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3772** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3777** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3783** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3785** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3807** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3810** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3846** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3912** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3955** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3964** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3972** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3977** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3983** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3990** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 3994** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4039** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4096** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4113** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4141** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4153** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4161** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4178** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4213** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4239** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4244** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4250** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4253** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4273** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4289** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4309** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4337** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4361** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4387** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4394** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4400** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4404** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4466** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4518** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4523** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4538** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4569** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4578** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4584** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4599** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4607** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4608** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4610** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4676** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4696** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4734** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4761** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4800** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4805** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4824** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4882** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4953** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4955** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 4956** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5012** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5015** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5038** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5050** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5057** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5096** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5106** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 5108** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5121** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5124** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5126** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5138** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5161** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5166** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5185** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5204** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5248** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5260** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5267** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5270** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5321** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5327** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5350** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5379** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5382** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5459** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5466** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5529** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5533** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5577** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5629** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5650** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5692** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5710** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5737** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5744** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5765** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5774** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5817** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5868** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5927** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5953** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 5992** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6020** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6061** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6068** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6085** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6093** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6122** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6133** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6222** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6258** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6316** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6346** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6363** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6396** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6397** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6475** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6478** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6504** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6513** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6532** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6553** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6559** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6563** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6572** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6599** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6605** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6655** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6704** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6715** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6758** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6853** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6861** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6895** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6916** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6933** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6940** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6948** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6968** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6971** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6974** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6975** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 6988** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7055** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7121** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7133** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7146** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7161** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7194** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7213** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7215** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7246** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7260** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7307** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7316** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7328** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7393** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 7462** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7500** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7505** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7509** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7538** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 7583** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7621** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7634** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7668** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7693** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7727** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7753** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7839** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7887** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7905** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 7984** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8009** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8039** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8047** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8074** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8075** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8095** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8121** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8133** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8149** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8158** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8182** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8183** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8246** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8247** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8262** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8279** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 8306** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8320** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8361** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8385** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8390** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8442** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8454** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 8516** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8573** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8620** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8672** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8673** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8699** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8748** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8763** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8846** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8858** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8883** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8929** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 8942** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9017** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9022** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9026** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9050** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9077** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9218** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9229** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9235** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9306** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9323** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9349** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9363** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9385** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9410** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9428** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9432** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9465** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9469** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9504** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9518** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9535** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9559** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9600** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9631** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9640** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9648** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9684** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9688** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9703** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9704** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9706** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9715** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9765** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9830** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9890** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9917** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9929** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9954** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 9995** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10032** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10042** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 10118** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10126** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10133** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10173** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10181** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10198** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10206** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10215** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10218** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10246** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10251** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10260** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10307** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10314** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10321** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 10339** :

- is characterized by the factor(s) :
*etude_temps_plein_Oui*.

**The individual 63** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 140** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 209** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 277** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 299** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 385** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 451** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*, *emprunt_gouv.NA* (factors are sorted from the strongest).

**The individual 565** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 863** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 975** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 987** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 1454** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 1626** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 1696** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 1701** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 1923** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 1955** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 2127** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 2194** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 2200** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 2338** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 2494** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 2534** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 2678** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *satisfaction_emploi_Non* (factors are sorted from the strongest).

**The individual 2834** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 3082** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 3442** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 3676** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 3856** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 4258** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 4819** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 4974** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 5082** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 5086** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 5313** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 5345** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 5425** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 5567** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 5623** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 5859** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 5928** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 6126** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 6197** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 6483** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 6586** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 6737** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 6775** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*, *emprunt_gouv.NA* (factors are sorted from the strongest).

**The individual 6846** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 6867** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 7054** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 7100** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 7487** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 7615** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 7873** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 7948** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 7957** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 8098** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 8181** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 8319** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 8323** :

- is characterized by the factor(s) :
*etude_temps_plein.NA*.

**The individual 8466** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 8534** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*, *satisfaction_emploi_Non* (factors are sorted from the strongest).

**The individual 8621** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 8634** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 8737** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 9052** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 9099** :

- is characterized by the factor(s) :
*emprunt_gouv.NA*.

**The individual 9379** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 9382** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 9458** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*, *satisfaction_emploi_Non* (factors are sorted from the strongest).

**The individual 9533** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 9611** :

- is characterized by the factor(s) :
*satisfaction_emploi_Non*, *etude_temps_plein_Oui* (factors are sorted from the strongest).

**The individual 9717** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 10166** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

**The individual 10268** :

- is characterized by the factor(s) :
*scolarite_obtenue_2010.NA*.

These outliers are suppressed from the analysis and a second one is performed on the rest of the individuals.

- - -

### 2. Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of analyse express **27.11%** of the total dataset inertia ; that means that 27.11% of the individuals (or variables) cloud total variability is explained by the plane.
This is a small percentage and the first plane just represents a part of the data variability.
This value is greater than the reference value that equals **26.01%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 428 data tables of equivalent size on the basis of a uniform distribution).

From these observations, it is interesting to consider the next dimensions which also express a high percentage of the total inertia.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
ggplot2::ggplot(cbind.data.frame(x=1:nrow(res$eig),y=res$eig[,2])) + ggplot2::aes(x=x, y=y)+ ggplot2::geom_col(fill="blue") + ggplot2::xlab("Dimension") + ggplot2::ylab("Percentage of variance") + ggplot2::ggtitle("Decomposition of the total inertia") + ggplot2::theme_light() + ggplot2::theme(plot.title = ggplot2::element_text(hjust =0.5)) + ggplot2::scale_x_continuous(breaks=1:nrow(res$eig))
```

**Figure 2 - Decomposition of the total inertia**

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 2 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (27.11% against 26.01%).
This observation suggests that only these axis are carrying a real information.
As a consequence, the description will stand to these axis.

- - -

### 3. Description of the plane 1:2

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
res.MCA<-MCA(entrain_valid[1:19][,-c(8,10,12,13,16,17,18)],quanti.sup=c(1,12),quali.sup=c(2,3,4,5,6,7),graph=FALSE)
plot.MCA(res.MCA,select= 'contrib 10342',selectMod= 'contrib  4 ',habillage='contrib',col.quali.sup='#006400',title="Nature Sociodmographique",cex=0.8,cex.main=0.8,cex.axis=0.8,label ='none')
```

**Figure 3.1 - Individuals factor map (MCA)**

The Wilks test p-value indicates which variable factors are the best separated on the plane (i.e. which one explain the best the distance between individuals).
```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
wilks.p <-
c(scolarite_avant = 0, langue = 1.84306797281362e-180, scol_mere = 1.05234911629255e-109, 
scol_pere = 2.29544825572497e-106, minorite_visible = 1.58150246420309e-83, 
genre = 5.0627955253176e-06)
wilks.p
```
The best qualitative variable to illustrate the distance between individuals on this plane is : *scolarite_avant*.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
sample = sample(rownames(res$call$X), length(rownames(res$call$X)))
res$call$X = res$call$X[sample,]
res$ind$coord = res$ind$coord[sample[!sample %in% rownames(res$ind.sup$coord)],]
res$ind.sup$coord = res$ind.sup$coord[sample[sample %in% rownames(res$ind.sup$coord)],]
drawn <-
integer(0)
hab <-
"scolarite_avant"
par(mar = c(4.1, 4.1, 1.1, 2.1))
plotellipses(res, axes = 1:2, invisible = c('var', 'quali'), select = drawn, keepvar = hab, title = '', cex = cex)
```

**Figure 3.2 - Individuals factor map (MCA)**
*The labeled individuals are those with the higher contribution to the plane construction.*
*The individuals are coloured after their category for the variable* scolarite_avant.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
